A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2020-02-06 paper.Rmd
keep_tex: true

---
title: A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.
author: Nicholas J Tierney\* (1,2) & Karthik Ram\* (3)
output:
  bookdown::pdf_document2:
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
header-includes: 
  - \linespread{2} 
  - \usepackage[utf8]{inputenc}
---

>>>>

---
title: A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.
author: Nicholas J Tierney\* (1,2) & Karthik Ram\* (3)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
header-includes: 
  - \linespread{2} 
  - \usepackage[utf8]{inputenc}
---
